Influence of Multi-Axial Stress States on the Flexural Behaviour of Circular Concrete-Filled Steel Tubes

### 2018-03-26 Paper7.tex
mac

	\begin{abstract}
		The paper proposes the methodologies and the equations to consider the influence of multi-axial stress states on material strength of circular Concrete-filled Steel Tubular (CFST) columns. From the previous experimental and numerical studies on the flexural behaviour of circular CFST members, the combination of multi-axial stress states, namely the concrete confinement effects and the steel bi-axial stress state, was found to benefit the bending capacity of CFST columns. Therefore, the bending capacity of the CFST columns will be underestimated by the Distributed Plasticity (DP) model when uni-axial material properties are used. To account for the material strength variation under multi-axial stress states and to improve the accuracy of the DP model, material strength correction methods were proposed based on the analytical results given by the 3D Finite Element (FE) model. A comprehensive parametric study, which involved a wide range of diameter-thickness ratios, material properties and axial load levels, had been carried out to study the influence of CFST cross-section properties on the multi-axial stress states. Based on the parametric study, the confined concrete strength under bending was found to be independent on the constant axial load level. On the contrary, the steel bi-axial stress was proved to be sensitive to the constant axial load level. A section factor $\xi$ was used to represent both the geometry and material properties of a CFST cross-section. With statistic operations, $\xi$-dependent correction equations were derived to account for the material strength variation under multi-axial stress states. The feasibility of the proposed material strength correction equations was verified to be good for both the design and modelling of circular CFST members.
	\end{abstract}

@@

	The behaviour of concrete-filled steel tubes (CFSTs) is governed by the contribution of the steel tube and the concrete core. As concluded from previous experimental studies (Silva et al. 2016 \cite{Silva2016}), The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved. Besides its excellent ductility, the composition of concrete and steel will also cause the two components under multi-axial stress state and thus, lead to the material properties variance. The steel tube provides the confined stress to the concrete core and make it under tri-axial stress state, which is well known as concrete confinement effect. The strength and ductility of the concrete core are enhanced by the confinement effect, therefore, the capacity of CFST member under either compression or bending is benefited.

@@

	In recent years, there were many researchers had investigated the concrete confinement effect of CFST members. Based on the test results, Sakino et al. 2004 \cite{RN41}, Fujimoto et al. 2004 \cite{RN15} and Inai et al. 2004 \cite{RN30} had tested circular and rectangular CFST columns under axial compressive loading, eccentric compressive loading and bending, respectively. All the researchers figured out that, the circular CFST members had a more significant concrete confinement effect than the rectangular columns. Hu et al. 2003 \cite{RN1} and Hu et al. 2005 \cite{RN29} had derived the equations to calculate the confined concrete strength under either compression or bending. The concrete confinement effect of CFST member was found to be sensitive to its diameter-thickness ratio.
	Due to the expansion of concrete core, the steel tube of CFST will also be under bi-axial stress state when loaded. The multi-axial stress state will change the steel yield stress under compression and tension. In the research works of Fujimoto et al. 2004 \cite{RN15}, Inai et al. 2004 \cite{RN30} and Lai and Varma 2016 \cite{RN32}, a reduction of steel yield stress had been made when the CFST was under compression. While for the tensile yield stress of steel, Fujimoto et al. 2004 \cite{RN15} and Inai et al. 2004 \cite{RN30} considered that the bi-axial stress state would have a positive influence on the tensile yield stress of the steel, and thus, an modification on their values was necessary.

@@

	Regarding the Eurocode 4 \cite{RN64} design provision, the confined concrete strength and the corrected steel yield stress are considered. However, the code clearly targets this consideration for member under compression, whilst being very restrictive for bending combined with compression. When it comes to fully flexural loads, the codes does not consider any effect of multi-axial stress states to exist.

>>>>

	\begin{abstract}
		The paper proposes the methodologies and the equations to consider the influence of multi-axial stress states on the material strength of circular Concrete-filled Steel Tubular (CFST) columns. From the previous experimental and numerical studies on the flexural behaviour of circular CFST members, the combination of multi-axial stress states, namely the concrete confinement effects and the steel bi-axial stress state, was found to benefit the bending capacity of CFST columns. Therefore, the bending capacity of the CFST columns will be underestimated by the Distributed Plasticity (DP) model when uni-axial material properties are used. To account for the material strength variation under multi-axial stress states and to improve the accuracy of the DP model, material strength correction methods were proposed based on the analytical results given by the 3D Finite Element (FE) model. A comprehensive parametric study, which involved a wide range of diameter-thickness ratios, material properties and axial load levels, had been carried out to study the influence of CFST cross-section properties on the multi-axial stress states. Based on the parametric study, the confined concrete strength under bending was found to be independent on the constant axial load level. On the contrary, the steel bi-axial stress was proved to be sensitive to the constant axial load level. A section factor $\xi$ was used to represent both the geometry and material properties of a CFST cross-section. With statistic operations, $\xi$-dependent correction equations were derived to account for the material strength variation under multi-axial stress states. The feasibility of the proposed material strength correction equations was verified to be good for both the design and modelling of circular CFST members.
	\end{abstract}

@@

	The behaviour of concrete-filled steel tubes (CFSTs) is governed by the contribution of the steel tube and the concrete core. As concluded from previous experimental studies (Silva et al. 2016 \cite{Silva2016} and Silva et al. 2017 \cite{RN140}), The concrete core constrains the steel tube to its interior, thus delaying the occurrence of the local buckling to higher levels of deformation and the ductility of the steel tube is improved. Besides its excellent ductility, the composition of concrete and steel will also cause the two components under multi-axial stress state and thus, lead to the material properties variance. The steel tube provides the confined stress to the concrete core and make it under tri-axial stress state, which is well known as concrete confinement effect. The strength and ductility of the concrete core are enhanced by the confinement effect, therefore, the capacity of CFST member under either compression or bending is benefited. In recent years, there were many researchers had investigated the concrete confinement effect of CFST members. Based on the test results, Sakino et al. 2004 \cite{RN41}, Fujimoto et al. 2004 \cite{RN15} and Inai et al. 2004 \cite{RN30} had tested circular and rectangular CFST columns under axial compressive loading, eccentric compressive loading and bending, respectively. All the researchers figured out that, the circular CFST members had a more significant concrete confinement effect than the rectangular columns. Hu et al. 2003 \cite{RN1} and Hu et al. 2005 \cite{RN29} had derived the equations to calculate the confined concrete strength under either compression or bending. The concrete confinement effect of CFST member was found to be sensitive to its diameter-thickness ratio. Regarding Eurocode 4 \cite{RN64}, the concrete confinement effect of circular CFST members is considered in both compressive and bending cases.

@@

	Due to the expansion of the concrete core, the steel tube of CFST will be under bi-axial stress state when the member is loaded. The bi-axial stress state will have an influence on the steel yield stress. According to the research works of Fujimoto et al. 2004 \cite{RN15} and Inai et al. 2004 \cite{RN30}, the bi-axial stress state was found to have a positive effect on the steel tensile yield stress and a negative influence on the steel  compressive yield stress. Regarding the Eurocode 4 \cite{RN64} design provision, it considers a reduction of the steel yield stress when calculating the circular CFST column's plastic resistance to compression. While for the consideration of the flexural resistance of the circular CFST member, the Eurocode 4 is very restrictive since the codes does not consider any effect of steel bo-axial stress state to exist.

@@
